FAIR theory: Applying Open Science Principles to the Construction and Iterative Improvement of Scientific Theories

### 2025-01-06 dk_example/example.tex
add short textual description
add to dk example

\section{Ontology}
The constructs used are
\begin{itemize}
 \item performance
 \item performance accessment
 \item skill
 \item confidence
\end{itemize}

@@

>>>>

\section{Description}
The Dunning-Kruger effect is stated in terms of skill and overconfidence to show that measurement error can cause significant bias in the relationship between performance and overestimation.
Instrumental variable methods can be used to correct for this bias.

\section{Ontology}
The constructs used are
\begin{itemize}
 \item performance as a test score
 \item performance estimation as the difference between the expected and the actual test score
 \item skill as the ability to perform well on a given test
 \item overconfidence as the difference between self-assessed and actual skill
 \item measurement error as luck on a test
\end{itemize}

\section{Relationships}

\subsection{Original DK Paper}

\begin{figure}[ht]
  \vspace{1cm}
  \begin{center}
  \input{figures/original_dk.tex}
  \end{center}
  %\caption{Subtypes of `AbstractSem`.}
  \label{fig:typetree}
\end{figure}

With $-$ signifying a negative association and $\simeq$ meaning measured by.

\begin{itemize}
 \item low skilled are more overconfident in assessing their skill than high skilled
\end{itemize}

@@

\subsection{Correction}
There are different ways to correct for the bias introduced by measurement error:
\begin{itemize}
 \item use different test performances to calculate skill and overconfidence, but a small test-retest correlation can bias the estimate towrds zero then (Krueger and Mueller, 2002)
\end{itemize}
